Supporting Information : Effect of copula on extinction risk

### 2019-02-25 SuppMat.Rmd
modified

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker__risk_global_disp}](./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_d0}](./Results/ricker_scl_1/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199, scl=1); numlocs=5, numsteps=25, numsims=10000\label{fig_hassell_risk_d0}](./Results/hassell_scl_1/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r fig_pennycuick_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_pennycuick_risk_d0}](./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }

>>>>

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_global_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_d0_scl_1}](./Results/ricker_scl_1/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell_scl_1}](./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell_scl_1}](./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199, scl=1); numlocs=5, numsteps=25, numsims=10000\label{fig_hassell_risk_d0_scl_1}](./Results/hassell_scl_1/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r fig_pennycuick_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_pennycuick_r_vary_scl_1}](./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_pennycuick_r_vary_scl_1}](./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_pennycuick_risk_d0_scl_1}](./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }
